Enhancement of SDR in Thessaloniki

### 2024-03-24 GHI_enh_04_investigate.tex
Commit 2024-03-24 21:12

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-20}

@@

@@

\begin{verbatim}
2024-03-20 09:43:30.5 athan@tyler GHI_enh_04_investigate.R 1.065564 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-24}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-groups-bin2d-4} \end{center}

@@

\begin{verbatim}
2024-03-24 18:26:30.5 athan@tyler GHI_enh_04_investigate.R 2.229609 mins
\end{verbatim}
